How many researchers use 'boilerplate' statistical analysis sections?

### 2021-03-12 manuscript/draft_manuscript.Rmd
Update draft_manuscript.Rmd

>>>>

Many researchers are using lazy practice by copying a standard "boilerplate" statistical methods section, likely cut-and-pasting from other researchers or projects. This is a strong sign of the ritualistic practice of statistics where researchers go through the motions rather than using conscientious practice [@Stark2018]. This is concerning because using the wrong statistical methods can reduce the potential of study, or worse, invalidate the entire study. Poor statistical practice is a key driver of the ongoing reproducibility crisis in science [@Ioannidis2014].
